---
title: "Tidying up"
output:
  pdf_document: default
  html_document: default
---
This is code to deal with a partial model run. When you run a model, something might crash, leaving you with a partial number of replicates. You'll need to figure out which replicate was full run. Then keep elements of the data matrices that are less than or equal to that number. 


You will need to modify 2 things
1.  The file path to read in the results
2.  The the number of the final replicate to keep (8 in this case.)



```{r setup, include=FALSE}
library("here")
here::i_am("postprocessing/economic/tidy_up_missing.Rmd")
source(here("processes","get_runinfo.R"))
source(here("processes","loadLibs.R"))



library("knitr")
library("viridis")
  #library("kableExtra")
library("tidyverse")
library("data.table")
options(knitr.kable.NA = '')
knitr::opts_chunk$set(echo = TRUE)

st<-"results_2024-08-22-12-04-23"

```



```{r replicate_pick_definition}

replicate_pick<-function(x){
  if (length(x)<=190){
    x<-x
  } else{
  
    if (dim(x)[[1]]==10){
      if (length(dim(x))==2){
          x<-x[1:8,]
      } else if (length(dim(x))==3){
          x<-x[1:8,,]
      }
    }
  }
}
```



```{r process_omval, include=FALSE}
# read in results file from omvalGlobal
omvalGlobal_filename<-list.files(path=here(st,"sim"), pattern="^omvalGlobal", recursive=FALSE)


for(i in 1:length(omvalGlobal_filename)){
  load(here(st,"sim", omvalGlobal_filename[i]))

  #Backup by appending "old" to the filename
  save(omvalGlobal, file=here(st,"sim", paste0("old", omvalGlobal_filename[i])), compress=FALSE)

  
    for (stock in 1:5){
      omvalGlobal[[stock]]<-lapply(omvalGlobal[[stock]],replicate_pick)
    }

  
  
  save(omvalGlobal, file=here(st,"sim", omvalGlobal_filename[i]), compress=FALSE)

   
}
```



```{r process_simlevel, include=FALSE}
# read in results file from omvalGlobal
simlevel_filename<-list.files(path=here(st,"sim"), pattern="^simlevelresults", recursive=FALSE)


for(i in 1:length(simlevel_filename)){
  simlevel<-readRDS(here(st,"sim", simlevel_filename[i]))

  
  
  #Backup by appending "old" to the filename
  saveRDS(simlevel, file=here(st,"sim", paste0("old", simlevel_filename[i])), compress=FALSE)

  
  simlevel<-lapply(simlevel,replicate_pick)
  
  saveRDS(simlevel, file=here(st,"sim", simlevel_filename[i]), compress=FALSE)

   
}





```












```{r Testing, include=FALSE}



# Testing
# omval1<-flLst[[1]]
# omval1$codGB$F_fullAdvice<-replicate_pick(omval1$codGB$F_fullAdvice)
# 
# omval1$codGB$ie_bias<-replicate_pick(omval1$codGB$ie_bias)
# 
# omval1$codGB$YEAR<-replicate_pick(omval1$codGB$YEAR)
# omval1$codGB$Rest<-replicate_pick(omval1$codGB$Rest)

# 
# for (stock in 1:5){
#   omval1[[stock]]<-lapply(omval1[[stock]],replicate_pick)
# }
# 
# 
# for(i in 1:length(omvalGlobal_filename)){
#   load(here(st,"sim", omvalGlobal_filename[i]))
#   flLst[[i]] <- omvalGlobal
# #  names(flLst[[i]]) <- names(omvalGlobal)
#   omvalGlobal<-NULL
# }


```


\newpage






